Introductory Physics Labs: A Tale of Two Transformations

### 2020-08-18 manuscript/onlineLabPaper.tex
Moved all section 4 material into manuscript and added info about practical exam to MS.

\section{Transformation \#1: Argument Driven Inquiry}
\textcolor{blue}{SFW mostly writes this.}

Brief lit review of ADI, including some of our prior work (PERC 2019 proceedings paper).
Describe the stages of ADI and how we implement them.

\section{Transformation \#2: Online Adaptation}
\subsection{Sudden Transition to Online Instruction--Spring 2020}

@@

Practical exams go in this paragraph!!!

>>>>

\section{Transformation \#2: Online Adaptation}

\subsection{Sudden Transition to Online Instruction--Spring 2020}

@@

We administered the lab practical exams for both courses in Canvas using GlowScript simulations embedded in Canvas assignments. Students made measurements on the simulation and used their results to make an argument answering a guiding question.
